### 2021-07-04 rad-icfp-2021/appendix1.tex
adding more examples
minor

\subsection{gradient from the introduction}

@@

Similarly to numpy, we use the notation OnesLike(A) to mean map (x -> 1) A 
and ZerosLike(A) to mean map (x -> 0) A. 
Finding these constant arrays is key to a lot of optimisations that leverage the ring algebraic structure of the reals to arrays.

@@

 \begin{proof}
The gradient of  derivative $\nabla_A$!sum(A)! is given by

    \begin{tabular}{c l r}
    & $\nabla_A$ !sum(A)! & \\
    = & $\nabla_A$ !reduce + 0 A! & \\
    $\defeq$ & \Big($\lambda$ !A',z. let A1 = scanl * 1 A in! \\
    & !let A2 = map2 (x,y -> 1) A1 A in! & \\
    & !let A3 = shift1 (map2 (x,y -> 1) A1 A) in! & \\
    & !let A4 = scanr * 1 A2 in! & \\
    & !map3 (a,b,c -> a+b*c*z) A' A4 A3! &
    &  \Big)(0,1) & \\
    $\stackrel{\beta-reduction}{=}$  & !let A1 = scanl * 1 A in! & \\
    & !let A2 = map2 (x,y -> y) A1 A in! & !A2=OnesLike(A)! \\
    & !let A3 = shift1 (map2 (x,y -> x) A1 A) in! & !A3=shift1 OnesLike(A)!\\
    & !let A4 = scanr * 1 A2 in! & \\
    & !map3 (a,b,c -> a+b*c*1) 0 A4 A3! & !map2 * A4 A3! & \\
    = & !let A1 = scanl * 1 A in! & \\
    & !let A2= OnesLike(A) in! &  \\
    & !let A3 = shift1 OnesLike(A) in! & !A3=OnesLike(A)! \\
    & !let A4 = scanr * 1 A2 in! & !A4=OnesLike(A2)! \\
    & !map2 * A4 A3! & \\
    = & !map2 * OnesLike(A) OnesLike(A)! & \\
    = & !OnesLike(A)!
    \end{tabular}
\end{align*}
 \end{proof}

>>>>

\subsection{gradient from the introduction}
\label{sub:gradintro}

@@

Similarly to numpy, we use the notation OnesLike(A) to mean map (x -> 1) A 
and ZerosLike(A) to mean map (x -> 0) A. 
Finding these constant arrays is key to a lot of optimizations that leverage the ring algebraic structure of the reals to arrays.

@@

 \begin{proof}
The gradient of !sum(A)! is given by

    \begin{tabular}{c l r}
    & $\nabla_A$ !sum(A)! & \\
    = & $\nabla_A$ !reduce + 0 A! & \\
    $\defeq$ & \Big($\lambda$ !A',z. let A1 = scanl * 1 A in! \\
    & !let A2 = map2 (x,y -> 1) A1 A in! & \\
    & !let A3 = shift1 (map2 (x,y -> 1) A1 A) in! & \\
    & !let A4 = scanr * 1 A2 in! & \\
    & !map3 (a,b,c -> a+b*c*z) A' A4 A3!\Big)(0,1) & \\
    $\stackrel{\beta-reduction}{=}$  & !let A1 = scanl * 1 A in! & \\
    & !let A2 = map2 (x,y -> y) A1 A in! & !A2=OnesLike(A)! \\
    & !let A3 = shift1 (map2 (x,y -> x) A1 A) in! & !A3=shift1 OnesLike(A)!\\
    & !let A4 = scanr * 1 A2 in! & \\
    & !map3 (a,b,c -> a+b*c*1) 0 A4 A3! & !map2 * A4 A3! \\
    = & !let A1 = scanl * 1 A in! & \\
    & !let A2= OnesLike(A) in! &  \\
    & !let A3 = shift1 OnesLike(A) in! & !A3=OnesLike(A)! \\
    & !let A4 = scanr * 1 A2 in! & !A4=OnesLike(A2)! \\
    & !map2 * A4 A3! & \\
    = & !map2 * OnesLike(A) OnesLike(A)! & \\
    = & !OnesLike(A)!
    \end{tabular}
\end{align*}
 \end{proof}

### 2021-07-04 rad-icfp-2021/correctness.tex
minor fixes
minor

 \begin{theorem}
     For every $\Gamma \vdash$ !e:!$\reals$, we have 
     $\sem{\grad_\Gamma e}= \grad_\Gamma\sem{e}$.
 \end{theorem}
where $\sem{-}$ is ab appropriate denotational semantics of smooth functions.

@@

In a similar vein, we form a concategory from the syntactic multicategory for Target.
We then use the universal property of $\ConcatT$ to construct a functor from $\ConcatT$ to this concategory.
This allows us to compare terms of Target UNF and terms of Target. 
$UNF^-1$ arises in this way.

>>>>

 \begin{theorem}
     For every $\Gamma \vdash$ !e:!$\reals$, we have 
     $\sem{\grad_\Gamma e}= \grad_\Gamma\sem{e}$.
 \end{theorem}
where $\sem{-}$ is an appropriate denotational semantics of smooth functions.

@@

In a similar vein, we form a concategory from the syntactic multicategory for Target.
We then use the universal property of $\ConcatT$ to construct a functor from $\ConcatT$ to this concategory.
This allows us to compare the terms of Target UNF and the terms of Target. 
$UNF^-1$ arises in this way.
